Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-04 ms.tex
changed out the aastex style file with one that doesn't skip first page.

% manuscript produces a one-column, double-spaced document:
%\documentclass[12pt,preprint]{aastex}
\documentclass[twocolumn]{aastex61}
%\documentclass[iop]{emulateapj}

@@

\shorttitle{KIC 12557548 b Long Term Followup}
\shortauthors{Schlawin et al.}

@@

\title{Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b}

@@

\author{J. Teske?}
\affiliation{Carnegie Observatories, 813 Santa Barbara Street, Pasadena, CA 91101, USA}

\author{S. Rappaport?}
\affiliation{MIT}

\author{R. van Lieshout?}
\affiliation{Institute of Astronomy - University of Cambridge}

\begin{abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
\end{abstract}

\keywords{stars: atmospheres -- stars: individual (\objectname{KIC 12557548}) -- stars: variables: general}

@@

\begin{deluxetable}{lr}
\tablecaption{List of observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Comment} \\
\colhead{UT} & \\
 }
\startdata
2016-06-10 & Clouds \\
2016-06-12 & Clear \\
2016-06-14 & Clear \\
2016-07-12 & Clear \\
2016-07-14 & Mostly clear \\
2016-07-16 & Clear \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
We obtained photometry for 5 nights with good weather on the \sha\ system.

>>>>

% manuscript produces a one-column, double-spaced document:
%\documentclass[12pt,preprint]{aastex}
\documentclass[preprint]{aastex61_mod}
%\documentclass[iop]{emulateapj}

@@

\shorttitle{KIC 12557548 b back to normal}
\shortauthors{Schlawin et al.}

@@

\title{Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b}

@@

\author{Jonathan Fraine?}
\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}

\author{Rafia Bushra?}
\affiliation{Steward Observatory, Tucson AZ 85721}

%\begin{abstract}
%KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
%We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
%\end{abstract}

%\keywords{stars: atmospheres -- stars: individual (\objectname{KIC 12557548}) -- stars: variables: general}

\section{Abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.

@@

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
The nights were clear with the exception of a few passing cloud son 2016-07-14.
We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
We obtained photometry for 5 nights with good weather on the \sha\ system.
